Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-09-03 Thesis/abstract.qmd
modify the front matter
update the declaration

This thesis includes one original paper published in a peer reviewed journal and two unpublished papers.

@@

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Coauthors are Monash students`,
  2, "A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol", "Published in the Journal of Computational and Graphical Statistics", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 5%", "No",
  3, "Automated Assessment of Residual Plots with Computer Vision Models", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  4, "Software for Automated Residual Plot Assessment: autovi and autovi.web", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 2.5%, K. Ackermann 2.5%", "No"
)

@@

>>>>

This thesis includes one original papers published in a peer reviewed journal and two unpublished papers. The core theme of the thesis is "automated reading of residual plots". The ideas, development and writing up of all the papers in the thesis were the principal responsibility of myself, the student, working within the Department of Econometrics and Business Statistics under the supervision of Professor Dianne Cook, Dr Emi Tanaka (Australian National University), Assistant Professor Susan VanderPlas (University of Nebraska–Lincoln) and Assistant Professor Klaus Ackermann.

@@

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Coauthors are Monash students`,
  2, "A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol", "Published in the Journal of Computational and Graphical Statistics", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 5%", "No"
  # 3, "Automated Assessment of Residual Plots with Computer Vision Models", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 2.5%, K. Ackermann 2.5%", "No",
  # 4, "Software for Automated Residual Plot Assessment: autovi and autovi.web", "To be submitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n E. Tanaka 5%, \n S. VanderPlas 2.5%, K. Ackermann 2.5%", "No"
)

@@

Chapters 3, *Automated Assessment of Residual Plots with Computer Vision Models*, and Chapter 4, *Software for Automated Residual Plot Assessment: autovi and autovi.web*, are planned for submission to peer-reviewed journals.

\clearpage

To ensure the clarity and coherence of the written content, artificial intelligence tools were employed to assist in smoothing and refining the language throughout the thesis.
